---
title: "example"
author: "Zhang chunxu"
date: "2024-12-07"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Distributed Robust Optimization and Sharpe Ratio Statistical Inference

This vignette introduces two key functionalities provided in this R
package: 1. **Distributed Robust Optimization Solver**: Solves a
distributed robust optimization problem by minimizing the objective
function. 2. **Sharpe Ratio Statistical Inference**: Computes the
p-value for statistical inference on Sharpe ratios between two datasets.

These tools provide powerful support for financial optimization and
statistical analysis.

------------------------------------------------------------------------

## Distributed Robust Optimization Function

Robust optimization is widely used to address uncertainty in
optimization problems. This function solves the following problem:

$$
\min_{\phi\in\mathcal{F}_{\delta,\bar{\alpha}}(n)}\max_{P\in\mathcal{U}_{\delta}(P_{n})}\{\phi^{T}Var_{P}(R)\phi\}
$$

The problem is equivalent to the following dual problem which is tractable.(Blanchet, J., Chen, L., & Zhou, X. Y. (2022))

$$
\min_{\phi\in\mathcal{F}_{\delta,\bar{\alpha}}(n)}\left(\sqrt{\phi^{T}Var_{P_{n}}\left(R\right)\phi}+\sqrt{\delta}||\phi||_{p}\right)^{2}
$$

The `opt_w` function (defined in `opt_w.R`) implements the above
optimization and gives a serie of earning rates using the `Rolling horizon` 
method as well as difference of the optimal weights so that 
we can evaluate the transaction costs.

### An example
```{r}
# Load the data from the .rda file
load(system.file("data", "data.rda", package = "SA24204169"))
d <- dim(data)[2] #dim of the data
w0 <- rep(1/d,d) # Initial weight
n <- 120 # Window
delta <- 1e-3 # Robustness parameter
alpha <- -0.1 # Adjusted expected return

result <- SA24204169::optimize_weights(data, w0, n, delta, alpha)
result
hist(result$returns, main = "Distribution of earning rates", xlab = "Returns")
```

------------------------------------------------------------------------

## Sharpe Ratio Statistical Inference Function


The Sharpe ratio is a key metric for assessing portfolio performance.
The `pvalue` function calculates the p-value for statistical inference
on Sharpe ratios between two datasets, helping to evaluate the
significance of portfolio performance differences.The method we applied is 
from Jobson & Korkie (1981).

### Example
```{r}
set.seed(0)
r1 <- result$returns # returns we get above
r2 <- rnorm(length(r1)) # simulated data for convenience
SA24204169::pvalue(r1,r2)

```

------------------------------------------------------------------------

This R package provides robust tools for financial optimization and
statistical analysis: - The **Distributed Robust Optimization** function
addresses constrained optimization problems. - The 
**Sharpe Ratio Statistical Inference** function offers a statistical test for Sharpe
ratio differences.

Users can extend these functions for broader applications in financial
analytics.

------------------------------------------------------------------------

## Reference

Blanchet, J., Chen, L., Zhou, X. Y. Distributionally robust mean-variance
portfolio selection with Wasserstein distances[J]. Management Science,
2022, 68(9): 6382-6410.

Jobson, J. D., Korkie, B. M. Performance hypothesis testing with the
Sharpe and Treynor measures[J]. Journal of Finance, 1981, 36: 889-908.
